Issues with Dynamical Measurements Across the Disk

### 2019-03-07 paper/ms.tex
Update dphi fig caption
Add thin-disk solar neighb

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to $\pm\Delta\phi/2$.
A cartoon explanation of this Figure is given in
Figure~\ref{fig:fig_to_explain}.}
\label{fig:range_deltaphi}
\end{figure*}

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi >$ XX, YY, and ZZ radians, with
corresponding physical scales of $\lambda \sim$ XX, YY, and ZZ parsecs. These
can be considered estimates of the range of validity for an extension of the
locally determined axisymmetric coordinate system, at least when it comes to
the study of stars on quasi-circular orbits.

>>>>

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{The range of midplane heights encountered as a function of angular
width. At each angle $\phi$ from Figure~\ref{fig:midplane} we consider an
angular width of $\Delta \phi$ centered on $\phi$ and report the range of
midplane heights within that width. We repeat the procedure for each $\phi$
and plot the result as translucent gray lines. We also plot the mean range as
a solid blue line and the $\pm1\sigma$ lines as dashed blue lines. The upper
$x$-axis shows the chord length from the position $\phi$ to $\pm\Delta\phi/2$. The horizontal \thincolor{} and \thickcolor{} lines shows the midplane variation necessary to induce a $100\%$ error in $J_z$ for the thin-disk and thick-disk orbits, respectively.
A cartoon explanation of this Figure is given in
Figure~\ref{fig:fig_to_explain}.}
\label{fig:range_deltaphi}
\end{figure*}

From Figure \ref{fig:range_deltaphi} it is clear that the range of midplane
values spanned in a given $\Delta \phi$ quickly saturates at $\Delta \phi
\gtrsim \pi/2$ radians (i.e. one quarter of the way around the Galactic disk
from the Sun). At far smaller $\Delta \phi$ it reaches the level of deviation
required for an $\mathcal{O}(1)$ systematic error in $J_z$ for our fiducial
thin-disk-like orbit (\thincolor horizontal line in Figure
\ref{fig:range_deltaphi}). For the three simulations considered, the median
range exceeds this value at $\Delta \phi/\pi > 0.036, 0.047, 0.10\,\text{rad}$, with
corresponding physical scales of $\lambda \sim 465, 610, 1290\,\pc$ for m12i, m12f, and m12m, respectively. These
can be considered estimates of the range of validity for an extension of the
locally determined axisymmetric coordinate system, at least when it comes to
the study of stars on quasi-circular orbits.
